Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-05-29 neurips-20/cvx-flats.tex
Section 1.1 - added, rearranged, suggested. Moved consistency intro from Sec 3 to Sec 2.1

\subsection{Notation}
In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$.
For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
%discrete land
We use $\R$ to denote a report set; it is not necessary for $\Y = \R$.  
For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
A loss $\ell : \R \times \Y \to \reals$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{target loss} for which we want to construct a consistent surrogate $L$.
For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
We denote the surrogate loss $L : \reals^d \times \Y \to \reals$, and typically denote a surrogate report with $u$.

Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions; a property is simply a function mapping distributions over the outcome simplex to reports.
Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\simplex \toto \R$.
We call a property \emph{set-valued} if there is a $p \in \simplex$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.

@@

@@

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
%While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.
\bo{This will need some references!}
\paragraph{Background.}
A basic requirement of surrogate losses $L$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the original problem of interest.
We can show a learning problem is hard by showing that consistency is not possible without a certain amount of complexity -- here, dimensionality $d$ of the prediction space.
But consistency, which we formalize below, is not very tractable, so we seek more useful necessary conditions.
Ideally, such a condition would apply to all of the following settings:
\begin{itemize}
  \item The original prediction space is either discrete, e.g. a classification problem; or it is continuous, e.g. a regression or estimation problem.
  \item The original prediction problem is given either directly by a loss $\ell$, for which $L$ should be a surrogate; or it is given by a \emph{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
\end{itemize}
In particular, a highly-studied case consists of discrete prediction spaces along with original losses $\ell$, for example, surrogates for $0-1$ loss.
Here a notable more-tractable condition is \emph{calibration}, which has been used to prove lower bounds on dimension of consistent surrogates.\bo{references, etc}
An example is the \emph{feasible subspace dimension} approach of \bo{TODO}.

>>>>

\subsection{Notation}
We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{report space} (or prediction space) $\R$, which may be different from $\Y$.
For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.

In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate report with $u \in \reals^d$.
A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$.

Because the paper focuses heavily on conditional distributions over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
The probability simplex over $\Y$ is $\simplex$.
For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
For a distribution $p \in \simplex$, we denote the expected target loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.

\bo{What about introducing the quadrants here? Something like: ``Instead of a target loss, in some estimation problems, one is given a target \emph{property}: [say what a property is]. The goal is to learn $f$ that approximately outputs the property on the conditional distribution given $x$. Example: mean estimation, etc..."}
Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions; a property is simply a function mapping distributions over the outcome simplex to reports.
Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\simplex \toto \R$.
We call a property \emph{set-valued} if there is a $p \in \simplex$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.

@@

\subsection{Consistency} \label{subsec:consistency}

\bo{Citation help appreciated!}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the original problem of interest.
One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
We would like to be able to lower-bound this dimension for a given learning problem.
\bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky. Then the bullet points explain the different settings.}
But consistency, which we formalize in Section \ref{sec::consis-implies-indir}, is not very tractable.
Ideally, we would have a more useful condition that could apply to all of the following settings:
\begin{itemize}
  \item The original prediction space is either discrete, e.g. a classification problem; or it is continuous, e.g. a regression or estimation problem.
  \item The original prediction problem is given either directly by a loss $\ell$, for which $L$ should be a surrogate; or it is given by a \emph{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
\end{itemize}
We informally call the combinations of these characteristics the ``four quadrants'' of supervised learning problems.
For exmaple, one quadrant has problems that are continuous and specified by a property $\gamma$.
An example learning problem in this quadrant would be mean estimation: hypotheses should map $x$ to the mean of the conditional distribution $D_x$

In particular, a highly-studied case consists of discrete prediction spaces along with original losses $\ell$, for example, surrogates for $0-1$ loss.
Here a notable more-tractable condition is \emph{calibration}, which we discuss next.

@@

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
%While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.
